On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2025-11-28 char-4k-bound/char-4k-bound.tex
[4k3] Bibliography - n-dashes

N. H. Anning and P. Erdős, Integral distances, \emph{Bull. Amer. Math. Soc.} 51.\textbf{8} (1945), 598–600, \textsc{doi}: \href

@@

(2008), 2653–2676, \textsc{doi}: \href {https://doi.org/10.1080/00207160902993636} {\nolinkurl {10.1080/00207160902993636}},

@@

217–236.

@@

100–116, arXiv: \href {http://arxiv.org/abs/1906.11926} {\nolinkurl {1906.11926}}, \textsc{url}: \url

@@

2901–2909.

@@

Comput. Geom.} 9.\textbf{4} (1993), 427–432, \textsc{doi}: \href {https://doi.org/10.1007/bf02189331} {\nolinkurl

@@

G. B. Huff, Diophantine problems in geometry and elliptic ternary forms, \emph{Duke Math. J.} 15.\textbf{2} (1948), 443–453,

@@

Geom.} 39.\textbf{4} (2008), 786–790, \textsc{doi}: \href {https://doi.org/10.1007/s00454-007-9038-6} {\nolinkurl

@@

S. Kurz, On the characteristic of integral point sets in {$\mathbb {E}^m$}, \emph{Australas. J. Combin.} 36 (2006), 241–248,

@@

S. Kurz and R. Laue, Bounds for the minimum diameter of integral point sets, \emph{Australas. J. Combin.} 39 (2007), 233–240,

@@

S. Kurz and A. Wassermann, On the minimum diameter of plane integral point sets, \emph{Ars Combin.} 101 (2011), 265–287,

@@

S. Kurz et al., Constructing $7$-clusters, \emph{Serdica J. Comput.} 8.\textbf{1} (2014), 47–70, arXiv: \href

@@

\emph{SIAM J. Optim.} 16.\textbf{1} (2005), 193–219.

@@

математика и фундаментальная информатика, 2022, 114–115.

@@

H. Nozaki, Lower bounds for the minimum diameter of integral point sets, \emph{Australas. J. Combin.} 56 (2013), 139–143.

@@

J. Solymosi, Note on integral distances, \emph{Discrete Comput. Geom.} 30.\textbf{2} (2003), 337–342, \textsc{doi}: \href

@@

J. Solymosi and F. De Zeeuw, On a question of Erdős and Ulam, \emph{Discrete Comput. Geom.} 43.\textbf{2} (2010), 393–401,

@@

математического анализа и смежные вопросы»} 8 (2018), 5–6.%

@@

2018, 492–498.

@@

М. Смуров and А. Спивак, Покрытия полосками, \emph{Квант} \textbf{5} (1998), 6–12.

>>>>

N. H. Anning and P. Erdős, Integral distances, \emph{Bull. Amer. Math. Soc.} 51.\textbf{8} (1945), 598--600, \textsc{doi}: \href

@@

(2008), 2653--2676, \textsc{doi}: \href {https://doi.org/10.1080/00207160902993636} {\nolinkurl {10.1080/00207160902993636}},

@@

217--236.

@@

100--116, arXiv: \href {http://arxiv.org/abs/1906.11926} {\nolinkurl {1906.11926}}, \textsc{url}: \url

@@

2901--2909.

@@

Comput. Geom.} 9.\textbf{4} (1993), 427--432, \textsc{doi}: \href {https://doi.org/10.1007/bf02189331} {\nolinkurl

@@

G. B. Huff, Diophantine problems in geometry and elliptic ternary forms, \emph{Duke Math. J.} 15.\textbf{2} (1948), 443--453,

@@

Geom.} 39.\textbf{4} (2008), 786--790, \textsc{doi}: \href {https://doi.org/10.1007/s00454-007-9038-6} {\nolinkurl

@@

S. Kurz, On the characteristic of integral point sets in {$\mathbb {E}^m$}, \emph{Australas. J. Combin.} 36 (2006), 241--248,

@@

S. Kurz and R. Laue, Bounds for the minimum diameter of integral point sets, \emph{Australas. J. Combin.} 39 (2007), 233--240,

@@

S. Kurz and A. Wassermann, On the minimum diameter of plane integral point sets, \emph{Ars Combin.} 101 (2011), 265--287,

@@

S. Kurz et al., Constructing $7$-clusters, \emph{Serdica J. Comput.} 8.\textbf{1} (2014), 47--70, arXiv: \href

@@

\emph{SIAM J. Optim.} 16.\textbf{1} (2005), 193--219.

@@

математика и фундаментальная информатика, 2022, 114--115.

@@

H. Nozaki, Lower bounds for the minimum diameter of integral point sets, \emph{Australas. J. Combin.} 56 (2013), 139--143.

@@

J. Solymosi, Note on integral distances, \emph{Discrete Comput. Geom.} 30.\textbf{2} (2003), 337--342, \textsc{doi}: \href

@@

J. Solymosi and F. De Zeeuw, On a question of Erdős and Ulam, \emph{Discrete Comput. Geom.} 43.\textbf{2} (2010), 393--401,

@@

математического анализа и смежные вопросы»} 8 (2018), 5--6.%

@@

2018, 492--498.

@@

М. Смуров and А. Спивак, Покрытия полосками, \emph{Квант} \textbf{5} (1998), 6--12.
